%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.
%
% Modified by Martijn Bakker

% *die 2012-present op volgende regel zou nice zijn als dat op een regel kan net als bij de andere data
% *Ik zou je gemiddelde cijfers toevoegen, dat zegt veel over jou als student
% *niet duidelijk wélke academic skills honors covert
% *5% bij honours, top bij excellence. Consistentie
% *kun je bij high school wel majoring zeggen?
% *100/hoeveel mensen ben je uitgekozen, benadruk het nationale
% *Alles bij experiences stoppen is misschien niet wat je wil, voor Amerika is het volgens mij gebruikelijk om het op te delen in honors en extracurricular
% *Interests: bij computer, die zin kan beter naar je SoP, gewoon je skills noemen voldoet op een reume. 3D zou ik bij Computer betrekken. Van Computers zou ik Computer of skills maken.
% de bassoon, sea scouts, RC model zou ik samennemen in een kop interests, dat is gebruikelijker. Daar kan je ook nog iets bijzetten als sport, cultuur, of iets dergelijks

\documentclass[11pt,a4paper,sans]{moderncv} 		%  ('10pt', '11pt' and '12pt') ('sans' and 'roman')

\moderncvstyle{classic}                             % 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               	% 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[scale=0.91]{geometry}

% personal data
\name{Martijn}{Bakker}
\title{Haarlem, The Netherlands -- February 5, 1995}

\address{Toekomststraat 56}{7521 CT Enschede}{The Netherlands}
\phone[mobile]{+316~41~25~8446}                   	
\phone[fixed]{+3123~56~50~770}
\email{martijn.simon.bakker@hotmail.com}            


%\phone[fax]{+3~(456)~789~012}
%\homepage{www.johndoe.com}                         
%\social[linkedin]{test}							
%\social[twitter]{jdoe}                             
%\social[github]{https://bitbucket.org/Gladdyu}  
%\extrainfo{additional information}                 
%\photo[64pt][0.4pt]{picture}                       
%\quote{Some quote}                                 

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\makecvtitle

\section{Education}
\cventry{2012 -- present}{Advanced Technology}{University of Twente}{Enschede}{}{Advanced Technology is a broad engineering BSc programme, including mechanical and electrical disciplines. The programme also includes the commercial and social aspects of the technologies. I completed the propaedeutic year cum laude and I am currently focusing on the field of Computer Science through additional and elective courses.}
\cventry{Summer 2014}{International Summer School 2014}{The Chinese University of Hong Kong}{}{}{'International Business' and 'Evidence-Based Human Resource Management', attaining grades A and A-.}
\cventry{2013 -- present}{Honours programme, design track}{University of Twente}{Enschede}{}{The honours programme is offered to the top 5\% of UT students. It covers academic skills and the analysis and creation of designs for society in depth.}
\cventry{2012/2013}{Excellence stream}{University of Twente}{Enschede}{}{The excellence stream is an additional course covering more advanced mathematics, offered by the UT to top students}
\cventry{2006 -- 2012}{High school}{Atheneum College Hageveld}{Heemstede}{}{Majoring in both Health and Technology, cum laude.}


\section{Experiences}
\cventry{Q2 2014/2015}{Teaching assistant -- Intelligent Interaction Design}{Dr. M. Theune -- University of Twente}{}{}{Guiding tutorial sessions and checking assignments for the course on C++.}
\cventry{Summer 2014}{Netherlands Asia Honours Summer School}{Hong Kong \& Shanghai}{}{}{The NAHSS is a unique interdisciplinary program for 100 Dutch top students which contains 4 main aspects: attending a summer school, visiting both Dutch and Asian companies, gaining acquaintance with the cultures and conducting research commissioned by a NAHSS partner company, for me, KPN: "How can ICT aid in keeping elderly at home for longer, both in Holland and in China?"}
\cventry{2013/2014}{Commissioner of Music}{Musica Sylvestra Orchestra}{Enschede}{}{As board member, I handled selecting, obtaining and distributing sheet music to the members alongside with arranging concert locations.}
\cventry{Q4 2013/2014}{Teaching assistant -- Advanced Engineering}{Dr. R.M.J. van Damme -- University of Twente}{}{}{Guiding seminars and tutorial sessions on applications of differential equations in electronics and mechanics.}
\cventry{Q2 2013/2014}{Lab supervisor -- Thermodynamics}{Dr. H.K. Hemmes -- University of Twente}{}{}{Guiding laboratory work and grading of the resulting lab journals.}
\cventry{2011}{IELTS}{}{Amsterdam}{}{International English Language Testing System, band 8/9.}
\cventry{2010}{EUSO}{}{Nijmegen}{}{Third place at the national qualifiers for the European Union Science Olympiad.}


\section{Interests}
\cvitem{Computers}{I have always had an interest in computers and as such I spend the majority of my free time on computer science related topics and hacking various things together. The languages I am familiar with include C/C++, Matlab, Mathematica, Java, Haskell, PHP, SQL and HTML/CSS/JavaScript.}
\cvitem{3D}{Creating (photorealistic) 3D models and animations, using Blender, 3ds Max and Photoshop.}
\cvitem{Bassoon}{Played since age 9, currently play first bassoon for the Musica Sylvestra Orchestra.}
\cvitem{Sea scouts}{Sailing and organizing activities, including summer camps (Czech Republic, 2011 and Croatia, 2012)}
\cvitem{RC models}{At age 13 I built a RC sailboat from scratch.}


\end{document}

